In-silico molecular enrichment and clearance of the human intracranial space

### 2024-11-27 paper/main.tex
Update on lengthgit status -mar
Former-commit-id: 2cfaaa6f5d37908d108703d045f2b1895cc0f6a3

\begin{abstract}
\end{abstract}
\begin{document}

@@

\mer{MER: Target length: 5000 words, 4-6 figures: 600 words Intro. 1400 words Methods. 2000 words Results. 1000 words Discussion.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\mar{~ 2000 words and 7 subsections - around 300 words each?}
\begin{enumerate}
\item
  ``A digital twin'' for molecular enrichment and clearance in human intracranial spaces
\item
  CSF flow, the role of production versus no/cardiac/respiratory
  dispersive effects on tracer trajectories, flow bifurcation. With and without tentorium cerebellum.
\item
  ``The role'' of PVS flow speed
\item
  ``The role'' of PVS sheaths and permeability - does functional separation entail structural separation?
\item
  ``The role'' of PVS size (motivated by pathologies)
\item
  Clearance from the CSF spaces - with and without low pressure veins, but keeping the intrathecal source of solute. 
\item
  Clearance from the parenchyma: $c_0 = 1.0$. Different substances?
\end{enumerate}

>>>>

\begin{abstract}
``The abstract — which should be no more than 200 words long and contain
no references — should serve both as a general introduction to the
topic and as a brief, non-technical summary of the main results and
their implications.'' 
\end{abstract}
\begin{document}

@@

\mer{MER: Target length: 5000 words (Intro, Results, Discussion) plus <3000 words Methods: 800 words Introduction. 2800 words Results. 1800 words Discussion.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\mer{Update: ~2800 words and 7 subsections - around 300-450 words each?}
\begin{enumerate}
\item
  ``A digital twin'' for molecular enrichment and clearance in human intracranial spaces
\item
  CSF flow, the role of production versus no/cardiac/respiratory
  dispersive effects on tracer trajectories, flow bifurcation. With and without tentorium cerebellum.
\item
  ``The role'' of PVS flow speed
\item
  ``The role'' of PVS sheaths and permeability - does functional separation entail structural separation?
\item
  ``The role'' of PVS size (motivated by pathologies)
\item
  Clearance from the CSF spaces - with and without low pressure veins, but keeping the intrathecal source of solute. 
\item
  Clearance from the parenchyma: $c_0 = 1.0$. Different substances?
\end{enumerate}
